\section{Introduction}
\subsection{The problem}
\TODO{General bla bla about the parking problem}
\subsection{More specific problem description}
The parking robot can move either forwards, backwards or sideways. The length of
the parking space is 6 meters, and it is 3 meters wide. The robots have smaller
dimensions. Every action takes some time. Lifting a car takes 9 seconds,
lowering it will take 3 seconds. The speed of the robot is 2 meters per second,
when not carrying a car, and 1 meter per second, when loaded. Changing the
direction takes 3 seconds. It needs time to accelerate and de-accelerate. 

The last paragraph describes the information we received. However there is still
some room to interpret the acceleration of the robot. It is said that changing
direction takes 3 seconds. The interpretation we used, is that it takes 1.5
seconds to stop a robot moving at it's maximum speed. And another 1.5 seconds to
accelerate it to maximum speed in another direction. Maximum speed depends on
whether the robot is carrying a car or not, however it makes sense that the
acceleration of robot can be greater, when the mass is lower. Meaning that a
heavy loaded robot can accelerate to speed 1 meter per second and that the empty
robot can accelerate to speed 2 meters per second in the same time.

\begin{table}
    \begin{tabular}{| c | c |}
        \hline
        Action & time\\
        \hline
        Lift car & 9\\
        Drop car & 3\\
        \hline
    \end{tabular}
    \TODO{make this table nice}
    \caption{The table describing the times some action will take}
\end{table}
\subsection{Simplified discrete problem}
